LaMachine: A meta-distribution for NLP software

### 2019-01-28 docs/lamachine_clarin2018.tex
minor edits in intro and enhancement of abstract

\begin{abstract}
We introduce LaMachine, a unified Natural Language Processing (NLP) open-source software distribution to facilitate the
installation and deployment of a large amount of software projects that have been developed in the scope of the
CLARIN-NL project and its current successor CLARIAH. Special attention is paid to encouragement of good software
development practices and reuse of established infrastructure in the scientific and open-source software development
community. We illustrate the usage of LaMachine in an exploratory text mining project at the Dutch Health Inspectorate where LaMachine was applied to create a research environment for automatic text analysis for health care quality monitoring.
\end{abstract}

@@

Software is a key deliverable and a vital component for research in projects such as those under the CLARIN umbrella. It
is software that provides researchers the instruments to yield for their research. It is CLARIN's core mission to make
digital language resources, including software, available to the wider research community.

@@

LaMachine incorporates software providing different types of interfaces which, as seen above, typically address different audiences. Whilst we
attempt to accommodate both technical\footnote{Data scientists, DevOps, system administrators, developers.} and
less-technical audiences\footnote{The wider researcher community, particularly the Humanities; also educational
settings.}, there is a natural bias towards the former as lower-level interfaces are often a prerequisite to build
higher-level interfaces on. Depending on the \emph{flavour} (more on this later) of LaMachine chosen, it makes a good virtual research
environment for a data scientist, whether on a personal computer or on a computing cluster, a good development
environment for a developer or a good deployment method for production servers in for example CLARIN centres.  We
demonstrate how LaMachine can create a fully functioning and standalone research environment for text mining  and NLP
for Dutch texts in a use case project at the Healthcare Inspectorate.

@@

\section{Comparisons and alternatives}
\label{sec:comparisons}

@@

\section{Case studies}

\subsection{Text Mining for Health Inspection}
\label{sec:case}

>>>>

\begin{abstract}
We introduce LaMachine, a unified Natural Language Processing (NLP) open-source software distribution to facilitate the
installation and deployment of a large amount of software projects that have been developed in the scope of the
CLARIN-NL project and its current successor CLARIAH. Special attention is paid to encouragement of good software
development practices and reuse of established infrastructure in the scientific and open-source software development
community. We explain what Lamachine is, how it cn used and the technical details. We also compare Lamachine to alternative software distributions and discuss its advantages and limitations. We illustrate how LaMachine can be used in two case studies, one in an exploratory text mining project at the Dutch Health Inspectorate where LaMachine was applied to create a research environment for automatic text analysis for health care quality monitoring, and a second case where Lamachine was used to create a workspace for a one-week, intense collaboration by a diverse research team. 
\end{abstract}

@@

Software is a key deliverable and a vital component for research in projects such as those under the CLARIN umbrella. Software provides researchers the instruments to yield for their research. It is CLARIN's core mission to make
digital language resources, including software, available to the wider research community.

@@

LaMachine incorporates software providing different types of interfaces which, as seen above, typically address different audiences. Whilst we
attempt to accommodate both technical\footnote{Data scientists, DevOps, system administrators, developers.} and
less-technical audiences\footnote{The wider researcher community, particularly the Humanities; also educational
settings.}, there is a natural bias towards the former as lower-level interfaces are often a prerequisite to build
higher-level interfaces on. Depending on the \emph{flavour} (more on this later) of LaMachine chosen, it makes a good virtual research
environment for a data scientist, whether on a personal computer or on a computing cluster, a good development
environment for a developer or a good deployment method for production servers in for example CLARIN centres.

 This paper provides a detailed description of Lamachine, its purpose and functionality and the technical details. We discuss the advantages and limitations of Lamachine to alternative software distributions in Section \ref{sec:comparison}. We demonstrate how LaMachine can create a fully functioning and standalone research environment for text mining  and NLP for Dutch texts in two use cases in Section \ref{sec:case}.

@@

\section{Comparison to alternative distributions}
\label{sec:comparisons}

@@

\section{Case studies}\label{sec:case}

\subsection{Text Mining for Health Inspection}
